Regularising Lotka--Volterra Interaction Matrices by Species Grouping: Optimal Groupings Are Unpredictable

### 2021-10-24 article.rnw
Add a TODO with potential expansion for the methods/results.
Add the main result to the title of the article.
Add the abstract.

%Title Page
\title{Regularising Lotka--Volterra Interaction Matrices by Species Grouping}
\author{
	Christopher R. P. Brown
}
\date{}

@@

@@

>>>>

%Title Page
\title{Regularising Lotka--Volterra Interaction Matrices by Species Grouping: Optimal Groupings Are Unpredictable}
\author{
	Christopher R. P. Brown
}
\date{}

@@

\section*{Abstract}

Dynamic models of ecological communities require many parameters, making them expensive to fit.
To reduce the number of parameters, species are often divided into groups \emph{a priori}, using phylogeny or functional groups, and species within a group are assumed to behave identically.
Herein, I assess the validity of such grouping by deriving the optimal groupings \emph{a posteriori}, from the parsimony of a Lotka--Volterra model fit to fecundity data from six competing species of \emph{Drosophila} in laboratory conditions.
I find evidence that grouping can benefit the parsimony of species interaction models, but that there is no single optimal grouping.
Further, those groupings that did prove beneficial could not be predicted from information available \emph{a priori}, calling the method of \emph{a priori} species grouping into question.
Lastly, I find that species did not group equivalently in their competitive effect and in their response to competition, invalidating an assumption often made implicitly when defining species groupings.

@@

%TODO: Use Terry et al. table S1 for additional classification information. The two species that coclassify in both columns and rows are substantially larger.
